Securely and Privately Verifiable Protests

### 2018-06-05 poster/contents.tex
Updates the title
Restructures poster to fit updated figures

\begin{columns}
  \begin{column}{0.17\linewidth}
    \includegraphics[width=0.5\linewidth]{fig/kth_cmyk.eps}
    \hfill
  \end{column}
  \hfill
  \begin{column}{0.64\linewidth}
    \begin{center}
      \Huge\bfseries
      Securely and Privately Verifiable Protests
    \end{center}
    \begin{center}
      \large
      Daniel Bosk <dbosk@kth.se>
      $\bullet$
      Sonja Buchegger
      $\bullet$
      Sébastien Gambs
    \end{center}
    \vspace{1.5em}
  \end{column}
  \hfill
  \begin{column}{0.17\linewidth}
    \hfill
    \includegraphics[width=0.8\linewidth]{fig/uqam.pdf}
  \end{column}
\end{columns}

@@

\includegraphics[width=\linewidth]{art/ProtestVerif.png}

@@

    \begin{figure}
      \centering
      \includegraphics[width=0.9\linewidth]{fig/trump.jpg}
      \caption{%
        What can we trust?
        This picture was posted on Twitter (and linked from Reddit) to argue 
        that the news reporting on the participation count was \enquote{fake 
          news} and that Trump's supporters arrived later.
        Even if the picture labelled \enquote{REALITY} would be from the same 
        event (difficult to verify), it is difficult to accurately compare due 
        to the angle.
        Image: Reddit/The\_Donald, Twitter.
      }\label{TrumpInauguration}
    \end{figure}

@@

    \begin{greenblock}{Our approach}
      \begin{itemize}
        \item Provides a \emph{lower bound} of the participation count.
        \item This lower bound is cryptographically verifiable.
        \item Provides privacy based on anonymous credentials and 
          privacy-preserving proximity testing.
        \item The only added risk (over not using this) is if someone can use 
          your secret key.
        \item Requires only local connectivity during the protest.
        \item Requires no trust in the source (as in \cref{TrumpInauguration}), 
          only that IDs are issued correctly.
      \end{itemize}
    \end{greenblock}

    \includegraphics[width=\linewidth]{art/ProtestVerif-UN.png}

@@

    \begin{figure}
      \centering
      \includegraphics[width=\linewidth]{fig/Jacobs-method.jpg}
      \caption{%
        Jacobs Method, currently most used method.
        Divide into regions, estimate density in each region, sum up.
        Image: popularmechanics.com
      }\label{JacobsMethod}
    \end{figure}

@@

@@

    \begin{blackblock}{Our scheme, during protest (\cref{ProofShare}, top of 
        \cref{Protocol})}
      \begin{itemize}
        \item The organizer publishes the protest's manifesto.
        \item Each protester reads it, approves it, computes a protest (cause) 
          identifier (\(cid\)) to designate which protest they participate in.
        \item Each protester computes a personal identifier (\(pid\)), 
          unlinkable between protests,
        \item Each protester acts as witness (\(wid\), unlinkable between 
          protesters, \(wsig\)) for other protesters by creating 
          participation-proof shares.
        \item Proof shares vouches for temporal and spatial eligibility.
        \item A threshold-based number of valid shares is a valid proof.
      \end{itemize}
    \end{blackblock}

    \begin{blackblock}{Our scheme, after the protest (bottom of 
        \cref{Protocol})}
      \begin{itemize}
        \item Proof shares are committed to a blockchain as soon as possible.
        \item \Ac{NIZK} proofs of correctness of \(PRF\) computations and 
          validity of keys are submitted whenever convenient.
        \item Anyone can verify the proofs: eligibility, universal and 
          individual verifiability.
        \item Must be done for all shares and their \ac{NIZK} proofs.
        \item Count all \(pid\)s with valid proofs.
      \end{itemize}
    \end{blackblock}

    \begin{block}{More info}
      \centering
      \includegraphics[width=0.4\linewidth]{fig/qr.eps}
    \end{block}

@@

  \begin{column}{0.32\linewidth}
    \begin{figure}
      \centering
      \includegraphics[width=\linewidth]{fig/proofshare.tikz}
      \caption{%
        Structure of a proof share.
        The protester \(P\)'s identifier \(pid\) is computed using the protester's 
        key \(k_P\).
        The witness \(W\)'s identifier \(wid\) is computed using the witness's key 
        \(k_W\).
        \(t_s\) is a time interval and \(l\) is the coordinates of an area.
        The protest (cause) identifier \(cid\) is the hash value of the manifesto.
      }%
      \label{ProofShare}
    \end{figure}%

    \begin{figure}
      \centering
      \begin{minipage}{\linewidth}
        \begin{align*}
          O\to \text{all}\colon & \text{manifesto} \\
          P\colon & cid\gets H(\text{manifesto}), \\
          & pid\gets PRF_{k_P}(cid) \\
          P\to W\colon & pid \\
          W\leftrightarrow P\colon & \text{perform distance bounding} \\
          W\colon & wid\gets PRF_{k_W}(pid), \\
          & wsig\gets PRF_{k_W}(wid, t_s, l) \\
          W\to P\colon & (wid, t_s, l, wsig) \\[-1em]
          && \text{during protest} \\ \midrule && \text{after protest} \\[-1em]
          W\to S\colon & H(pid, wid, t_s, l, wsig) \\
          P\to S\colon & H(pid, wid, t_s, l, wsig) \\
          W\to S\colon & (pid, wid, t_s, l, wsig),\\
          & NIZK( wid = PRF_{k_W}(pid), \\
          & wsig = PRF_{k_W}(wid, t_s, l), \\
          & \exists sign(k_W)) \\
          P\to S\colon & (pid, wid, t_s, l, wsig),\\
          & NIZK(pid = PRF_{k_P}(cid), \exists sign(k_P))
        \end{align*}
      \end{minipage}
      \caption{%
        An overview of message exchanges.
        The organizer \(O\) broadcasts the manifesto.
        \(P\), \(W\) and their computations are as in \cref{ProofShare}.
        Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
      }%
      \label{Protocol}
    \end{figure}

>>>>

\begin{columns}
  \begin{column}{0.17\linewidth}
    \includegraphics[width=0.5\linewidth]{kth_cmyk.eps}
    \hfill
  \end{column}
  \hfill
  \begin{column}{0.64\linewidth}
    \begin{center}
      \Huge\bfseries
      From grassroots to CROCUS:\\[-0.25em]
      privacy-preserving CROwd Counting Using Smartphones
    \end{center}
    \vspace{0.25em}
    \begin{center}
      \large
      Daniel Bosk <dbosk@kth.se>
      $\bullet$
      Sonja Buchegger
      $\bullet$
      Sébastien Gambs
    \end{center}
    \vspace{1.5em}
  \end{column}
  \hfill
  \begin{column}{0.17\linewidth}
    \hfill
    \includegraphics[width=0.8\linewidth]{uqam.pdf}
  \end{column}
\end{columns}

@@

\includegraphics[width=\linewidth]{ProtestVerif.png}

@@

    \begin{figure}
      \centering
      \includegraphics[width=0.9\linewidth]{trump.jpg}
      \caption{%
        What can we trust?
        This picture was posted on Twitter (and linked from Reddit) to argue 
        that the news reporting on the participation count was \enquote{fake 
          news} and that Trump's supporters arrived later.
        Even if the picture labelled \enquote{REALITY} would be from the same 
        event (difficult to verify), it is difficult to accurately compare due 
        to the angle.
        Image: Reddit/The\_Donald, Twitter.
      }\label{TrumpInauguration}
    \end{figure}

@@

    \begin{greenblock}{Our approach}
      \begin{itemize}
        \item Provides a \emph{lower bound} of the participation count.
        \item This lower bound is cryptographically verifiable.
        \item Provides privacy based on anonymous credentials and 
          privacy-preserving proximity testing.
        \item Requires only local connectivity during the protest.
        \item Requires no trust in the source (as in \cref{TrumpInauguration}), 
          only that IDs are issued correctly.
      \end{itemize}
    \end{greenblock}

    \includegraphics[width=\linewidth]{ProtestVerif-UN.png}

@@

    \begin{figure}
      \centering
      \includegraphics[width=\linewidth]{Jacobs-method.jpg}
      \caption{%
        Jacobs Method, currently most used method.
        Divide into regions, estimate density in each region, sum up.
        Image: popularmechanics.com
      }\label{JacobsMethod}
    \end{figure}

@@

%    \begin{block}{More info}
%      \centering
%      \includegraphics[width=0.4\linewidth]{qr.eps}
%    \end{block}

@@

    \begin{blackblock}{Our scheme, during protest (\cref{ProofShare}, top of 
        \cref{Protocol})}
      \begin{itemize}
        \item The organizer publishes the protest's manifesto.
        \item Each protester reads it, approves it, computes a protest (cause) 
          identifier (\(\cid\)) to designate which protest they participate in.
        \item Each protester computes a personal identifier (\(\pid\)), 
          unlinkable between protests,
        \item Each protester acts as witness (\(\wid\), unlinkable between 
          protesters) for other protesters by creating participation-proof 
          shares.
        \item Proof shares vouches for temporal and spatial eligibility.
      \end{itemize}
    \end{blackblock}

    \begin{figure}
      \centering
      \includegraphics[width=\linewidth]{proofshare.tikz}
      \caption{\label{ProofShare}%
        Structure of a proof share.
        The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
        The protester \(P\)'s identifier \(\pid\) is computed using the 
        protester's key \(\sk_P\) and \(\cid\).
        The witness \(W\)'s identifier \(\wid\) is computed using the witness's 
        key \(\sk_W\) and \(\pid\).
        \(t_s, t_s'\) are the last heads of the blockchain seen by the 
        protester and witness, respectively, and \(l\) is an area.
        All values are signed by the witness while also proving the correctness 
        of \(\wid\) and knowledge of a signature on \(\sk_W\).
      }%
    \end{figure}%

@@

    \begin{blackblock}{Our scheme, after the protest (bottom of 
        \cref{Protocol})}
      \begin{itemize}
        \item Proof shares are committed to a blockchain as soon as possible.
        \item \Ac{NIZK} proofs of correctness (\(\prf_\pid, \prf_\wid\) in 
          \cref{Protocol}) of \(\ACprf\) computations and knwoledge of a valid 
          signature on the key are submitted whenever convenient.
        \item Anyone can verify the proofs: eligibility, universal and 
          individual verifiability.
        \item Must be done for all shares and their \ac{NIZK} proofs.
        \item Count all \(\pid\)s with valid proofs.
      \end{itemize}
    \end{blackblock}

    \begin{figure}
      \centering
      \begin{minipage}{\linewidth}
        \begin{align*}
          O\to \text{all}\colon & \text{manifesto} \\
          P\colon & t_s\gets \TSget \\
          & \cid\gets \Hash[\text{manifesto}], \\
          & \pid\gets \ACprf[_{\sk_P}][\cid] \\
          W\colon & t_s'\gets \TSget
          \\[-1em]
          \noalign{\hfill Join}
          \midrule
          \noalign{\hfill Participation}
          \\[-3em]
          P\to W\colon & \pid \\
          P\leftrightarrow W\colon &
          \PPK\mleft\{ (\sk_P) : \mright. \\
          & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
          & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
          \\
          W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
          W\to P\colon & (\wid, t_s', l)
          \\[-1em]
          \noalign{\hfill Participation}
          \midrule
          \noalign{\hfill Submission}
          \\[-2em]
          P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
          W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
          W\to S\colon & (\pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
          \text{where} \\
          & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
          & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
          & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
          \\
          & \qquad\qquad (\pid, \wid, t_s, t_s', l) \\
          P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid}),\quad 
          \text{where}\\
          & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
          & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
          & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
          \\
          & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
        \end{align*}
      \end{minipage}
      \caption{\label{Protocol}%
        An overview of the Join, Participation and Submission phases of \PRIVO.\@
        The organizer \(O\) broadcasts the manifesto.
        The protester \(P\), witness \(W\) and their computations are as in 
        \cref{ProofShare}.
        Finally, both \(P\) and \(W\) submits the proof shares to a permanent storage \(S\).
      }%
    \end{figure}
